---
mainfont: LiberationSerif
sansfont: LiberationSans
monofont: LiberationMono
output: 
  pdf_document:
    latex_engine: xelatex
    includes:
      in_header: "preamble.tex"
  html_document:
    theme: readable
geometry: top=0cm,bottom=0cm,left=3cm
urlcolor: blue
---

```{r setup, include=FALSE}
library(pictoralist)
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

# Load the source code for the figure of card A
card_env_A <- new.env()
source(file='fig_one_bar.R', local=card_env_A)

# No figure for card B
#
#

# Load data and define recipient (Use same performer as card 2)
data <- pictoralist::read_data('synth_data.csv')
recipient <- 'p2'
goal_rate <- 0.90

# get most recent performance of performer
filter <- data$id == recipient & data$time == max(data$time)
numerator <- data[filter,'numer'][[1]]
denominator <- data[filter,'denom'][[1]]
performance_percent <- paste(round(numerator/denominator, 3)*100, "%", sep="")

# Scale goal to observed denominator.  Truncate to single decimal place
goal_percent <- paste(100*goal_rate, "%", sep="")
scaled_goal <- round(denominator*goal_rate, 1)


```

<!-- CARD 3A -->
\vspace{2.0cm}\ 

**Card 3A**

Dear Alex,

You are a top performer this month for the measure [postoperative nausea and vomiting](https://mpog.org/files/quality/measures/ponv-03_spec.pdf) (PONV 03):

```{r figureA, fig.align='center', fig.width=4, fig.height=2.5, fig.showtext=TRUE}
  # Run figure generation
  card_env_A$run(recipient, data, "Peer Ave.")
```

\signoff
  
\vspace{2.5cm} 
...
\vspace{1.0cm} 

<!-- CARD 3B -->
**Card 3B**

Dear Alex,

You are a top performer this month for the measure [postoperative nausea and vomiting](https://mpog.org/files/quality/measures/ponv-03_spec.pdf) (PONV 03).

Your performance was `r performance_percent` (`r numerator`/`r denominator`), above the peer average of 90% (`r scaled_goal`/`r denominator`).

\signoff
